Sex-Specific Evolution of the Meiotic Recombination Rate

### 2020-07-30 doc/MS_v6.Rmd
overdue commits

---
title: 'Sex-Specific Evolution of the Meiotic Recombination Rate'
date: '`r Sys.Date()`'
author: "April L. Peterson, Bret A. Payseur"
output:
  word_document:
  pdf_document:
    keep_tex:  true
  html_document:
always_allow_html: yes
bibliography: refs_Main_Report.bib
csl: elife.csl
---

@@

```{r MAIN.TABLE1, echo=FALSE, eval=TRUE}

@@

>>>>

---
title: 'Sex-Specific Evolution of the Meiotic Recombination Rate'
author: "April L. Peterson, Bret A. Payseur"
output:
  word_document:
  pdf_document:
    keep_tex:  true
  header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
  html_document:
always_allow_html: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
bibliography: refs_Main_Report.bib
csl: elife.csl
---

@@

```{r MAIN.TABLE1, echo=FALSE, eval=FALSE}

@@

<SAC section 1>
